%-------------------------
% Nick Jaunich's Resume
% Author : Nick Jaunich
% License : PRIVATE
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

% Adjust footskip as per the warning by fancyhdr
% \setlength{\footskip}{4.08003pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Nick Jaunich} & Email: \href{mailto:panayao@gmail.com}{panayao@gmail.com} \\
  235 S Dixie Hwy Apt 910, Coral Gables, FL 33133 & Mobile: \href{tel:+16518080424}{(651) 808-0424} \\
\end{tabular*}

%-----------OBJECTIVE-----------------
\section{Objective}
  \resumeSubHeadingListStart
    \resumeSubItem{Objective}
      {Full-time opportunity in software development, mobile application development, or a related field, where expertise in leading technological development, innovation initiatives, and managing technical teams can be utilized to drive growth and deliver outstanding results.}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Wisconsin -- Madison}{Madison, WI}
      {Bachelor of Science in Computer Engineering}{Jan 2013 -- Dec 2017}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {American Express Company}{Sunrise, FL}
      {Senior Engineer II}{Jan 2024 -- present}
      \resumeItemListStart
        \resumeItem{Financial Crimes Platform}
          {Spearheading the development of American Express's next-generation Financial Crimes Platform, focusing on scalability, data integrity, and global compliance}
        \resumeItem{Modern JVM Languages and Frameworks}
          {Pioneering the adoption and integration of modern JVM languages and frameworks, particularly SpringBoot, to enhance the microservices architecture, resulting in improved performance and maintainability.}
        \resumeItem{API Development}
          {Leading API development with a focus on robustness and security, leveraging GraphQL. Driving forward the architecture for event-driven microservices using Kafka, enhancing real-time data processing.}
        \resumeItem{Polyglot Persistence}
          {Advocating for polyglot persistence to optimize data storage solutions, prominently using Oracle. Committing to the continuous evolution of the platform to combat financial crimes effectively.}
        \resumeItem{Mentorship}
          {Mentoring a team towards technical excellence, fostering an environment of learning and innovation. Collaborating across departments to navigate the complexities of AML regulations globally.}
      \resumeItemListEnd

    \resumeSubheading
      {My Logistics Solutions, Inc.}{Remote, USA}
      {Senior Software Engineer Team Lead}{Feb 2023 -- present}
      \resumeItemListStart
        \resumeItem{Technological Development and Innovation}
          {Leading the technological development and innovation initiatives for My Logistics Solutions' mobile and web platforms as the head of a dedicated team of 4 software engineers.}
        \resumeItem{Product Design}
          {Working closely with designers to refine and implement cutting-edge technical product designs using React, Next.JS, and React Native.}
        \resumeItem{Task Prioritization}
          {Strategizing and prioritizing tasks across the engineering team, fostering collaboration and efficiency.}
        \resumeItem{Modular Systems}
          {Architecting and building modular, reusable systems with a focus on performance and scalability using Sails.JS, Terraform, Kubernetes, Docker, and AWS.}
        \resumeItem{Continuous Contribution}
          {Continuously contributing to the software platform's development, launch, and maintenance, as well as providing other services to drive My Logistics Solutions' success.}
      \resumeItemListEnd

    \resumeSubheading
      {Kodiak LLC}{Remote, USA}
      {Senior Software Engineer}{Sept 2014 -- present}
      \resumeItemListStart
        \resumeSubSubheading{Tempest, Inc.}{Nov 2021 -- Mar 2023}
        \resumeItemListStart
          \resumeItem{Renewable Energy Startup}
            {Spearheading a renewable energy startup that leverages blockchain technology to empower individuals with decentralized investment into clean energy sources.}
          \resumeItem{Frontend Development}
            {Developing responsive frontend experiences and optimizing UI/UX using Next.JS and JSP.}
          \resumeItem{Backend Systems}
            {Architecting and building scalable backend systems with PHP, Laravel, and other technologies.}
          \resumeItem{AWS Infrastructure Management}
            {Managing AWS infrastructure, including deployment and orchestration using Terraform, Kubernetes, Docker, and CircleCI, to support the platform's growth and ensure high availability, reliability, and performance.}
        \resumeItemListEnd

        \resumeSubSubheading{Borokhim’s Oriental Rugs}{Sep 2014 -- present}
        \resumeItemListStart
          \resumeItem{AWS Infrastructure Management}
            {Managing and optimizing a robust AWS infrastructure to ensure seamless operation of the rug website and its inventory management system.}
          \resumeItem{SEO Strategies}
            {Implementing advanced organic SEO strategies for over 29,000 city landing pages, resulting in high search engine rankings across numerous cities in the United States.}
          \resumeItem{Twilio Integration}
            {Integrating Twilio services to facilitate effective communication with customers and support seamless business operations.}
        \resumeItemListEnd

        \resumeItem{Specialization}
          {Specializing in leading organizations’ technological development and innovation initiatives, translating complex technical concepts to non-technical stakeholders, and managing technical teams.}
        \resumeItem{Experience}
          {Leveraging over 8 years of software development experience and expertise in full-stack application design and development, working with cutting-edge technologies and industry best practices.}
        \resumeItem{Proficiency}
          {Demonstrating proficiency in various programming languages, frameworks, and libraries for web, mobile, and cloud-based solutions, including DevOps processes and tools.}
      \resumeItemListEnd

    \resumeSubheading
      {Chewy, Inc.}{Dania Beach, FL}
      {Senior Software Engineer}{May 2020 -- Jun 2021}
      \resumeItemListStart
        \resumeItem{SEO Team}
          {Senior Kotlin+Java Developer on the SEO team: Developed and implemented optimization strategies for Chewy.com to improve search engine results rankings using Quarkus Kotlin-based microservices. Conducted extensive keyword research to identify and integrate high-performing SEO keywords throughout the website.}
        \resumeItem{301 Redirects System}
          {Created a system for handling 301 redirects, seamlessly managing approximately a trillion possible URL permutations during the transition to "Clean URLs," using Kotlin-based microservices and event-driven architecture with event sourcing and CQRS principles.}
        \resumeItem{Spring Framework}
          {Leveraged Spring framework, including dependency injection, AOP, and Spring MVC for RESTful APIs, alongside reactive programming concepts (reactive streams, backpressure) using RxJava and Kotlin coroutines to build efficient and responsive applications at Chewy.}
        \resumeItem{Quarkus Kotlin Microservices}
          {Built, Dockerized, and deployed Quarkus Kotlin microservices on Kubernetes, streamlining application delivery, scaling, and management to ensure high availability and improved performance.}
        \resumeItem{Terraform Adoption}
          {Pioneered the adoption of Terraform within Chewy's AWS environment, significantly advancing infrastructure management by provisioning and scaling EKS clusters, managing ECS repositories, handling VPCs, and streamlining the creation of testing environments for storefront systems.}
        \resumeItem{Collaboration}
          {Actively collaborated with cross-functional teams, sharing expertise in Quarkus, Kotlin, Spring, Reactive programming, and containerization using Docker, Kubernetes, and Terraform to facilitate knowledge transfer and ensure best practices were followed throughout the organization.}
      \resumeItemListEnd

    \resumeSubheading
      {Target Corporation}{Minneapolis, MN}
      {Senior Software Engineer}{Jun 2016 -- Jun 2021}
      \resumeItemListStart
        \resumeItem{Ivy Promotions}
          {2018 -- 2021: Team Member of “Ivy Promotions”: team handling internal facing promotions creation/management interface. Development of Java RESTful APIs interfacing with Neo4j for the aggregation of promotion data for push to downstream consumers (Target stores) and the development of AngularJS-based UI frontend for creating and managing promotions by aggregating item, price, and inventory data from multiple internal data sources.}
        \resumeItem{ShopRight}
          {2017: Team Member of “ShopRight”: team handling competitive product pricing for Target.com and Target stores. Created various Java RESTful APIs using Spring Boot and reactive programming concepts (RxJava) for efficient and responsive services, which were responsible for managing different price-points for different Target stores.}
        \resumeItem{OrderUp!}
          {2016: Team Member of “OrderUp!”: team handling internal inventory transfer system. Assisting in development of AngularJS web application and Java Sprint Boot backend handling the transfer of products and stock between Target distribution centers and stores.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TECHNOLOGIES I USE-----------------
\section{Technologies I Use}
  \resumeSubHeadingListStart
    \resumeItem{Programming Languages}
      {C, C++, C\#, Java, Kotlin, Spring, Spring Boot, JavaScript (ES6), TypeScript, Python, Golang, HTML+CSS, Tailwind, Webpack, AngularJS, ReactJS, React Native, Vue.js, Node.js, Next.js, Vercel, jQuery, JSP, Laravel, Django, SQL, Neo4j, Cypher, AWS, GCP, Azure, PostgreSQL, MySQL, Terraform, CircleCI, Jenkins, Ansible, Artifactory, Bitbucket Pipelines (DevOps), Docker, Kubernetes, Nginx, Apache, PHP, Bash, CloudFlare, Axios}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
